TBD

### 2016-10-06 paper.tex
started adding Jacobian and Hessian
added simplify  GN section

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\bzero}{\bmath{0}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\subsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:red_least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bJ & \bJ^*\\
       \conj{\bJ}^* & \conj{\bJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bJ &= \frac{\partial \bv}{\partial \bz}, & \bJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator (cite Sorber).
The GN update step is now defined as:
\begin{equation}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. 
NEED TO MENTION THE SILENT INDEX $k$ AND HOW THE UPDATE RULE IS ITERATIVE. ALSO MENTION THAT $\lambda$ IMPROVES THE CONVERGENCE PROPERTIES. WE WILL REFER TO $\bJ^H\bJ$ AS THE 
HESSIAN.

@@

It is now trivial to compute the Hessian $\bJ^H\bJ$ by using Eq.~\eqref{eq:Jacobian_red}. If we substitute Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\bJ$
we obtain

>>>>

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\bzero}{\bmath{0}}
\newcommand{\conj}[1]{\overline{#1}}

@@

STILL NEEDS LOADS OF WORK. REFERENCES.

\subsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:red_least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bJ & \bJ^*\\
       \conj{\bJ}^* & \conj{\bJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bJ &= \frac{\partial \bv}{\partial \bz}, & \bJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator (cite Sorber).
The GN update step is now defined as:
\begin{equation}
\label{eq:GN_update}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. 
NEED TO MENTION THE SILENT INDEX $k$ AND HOW THE UPDATE RULE IS ITERATIVE. ALSO MENTION THAT $\lambda$ IMPROVES THE CONVERGENCE PROPERTIES. WE WILL REFER TO $\bJ^H\bJ$ AS THE 
HESSIAN.

@@

It is now trivial to compute the Hessian $\bJ^H\bJ$ by using Eq.~\eqref{eq:Jacobian_red}. If we substitute Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\bJ$
we obtain 
\begin{equation}
\bH = \bJ^H\bJ = 
\begin{bmatrix}
\bA & \bB\\
\conj{\bB} & \conj{\bA}
\end{bmatrix},
\end{equation}
where

\begin{align}
\bA &= \begin{bmatrix} \bC & \bD\\ \bD^H & \bE \end{bmatrix}, & \bB &= \begin{bmatrix} \bF & \bG\\ \bG^T & \bzero \end{bmatrix},
\end{align}

\begin{equation}
[\bC]_{ij} = 
\begin{cases}
 \sum_{k \neq i} \left | g_k \right |^2 \left | y_{\zeta_{ik}} \right |^2 & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
\begin{equation}
[\bD]_{ij} = 
\begin{cases}
 g_i y_j^*  \left | g_{\psi_{ij}} \right |^2  & \textrm{if} ~ \psi_{ij}\neq0\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}

\begin{equation}
[\bE]_{ij} = 
\begin{cases}
 \sum_{pq \in \mathcal{PQ}_i} \left | g_p \right |^2 \left | g_q \right |^2  & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
\begin{equation}
[\bF]_{ij} = 
\begin{cases}
 g_i g_j  \left | y_{\zeta_{ij}} \right |^2  & \textrm{if} ~ i \neq j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
and
\begin{equation}
[\boldsymbol{G}]_{ij} = 
\begin{cases}
 g_i y_j  \left | g_{\xi_{ij}} \right |^2  & \textrm{if} ~ \xi_{ij}\neq0\\
 0 & \textrm{otherwise}
\end{cases}.
\end{equation}

Moreover, $(*)^T$ denotes matrix transposition and

\begin{equation}
\mathcal{PQ}_i = \left\{pq\in\mathbb{N}^2|(\phi_{pq} = i) \right\}.
\end{equation}

\subsection{Simplifying GN}

The following identities,
\begin{align}
\label{eq:identities}
\frac{1}{3}\bJ\breve{\bz} &= \breve{\bv}, & \bJ^H\breve{\bv} &= (\bI\odot\bH)\breve{\bz} 
\end{align}
are trivially established by mechanically showing that the left hand side of each identity in Eq.~\eqref{eq:identities} is equal to its right hand side.

The first identity in Eq.~\eqref{eq:identities} can now be used to simplify Eq.~\eqref{eq:GN_update} as follows:
\begin{align}
\Delta \breve{\bz} &= (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv})\\
&=(\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}
\end{align}

HAVE TO MAKE SURE I DEFINE ALL THE MATH SYMBOLS THAT I USE. IF NOT HERE THEN EARLIER....
